Concept Dev for COMP study

### 2019-08-15 concept_dev.tex
updated base table with counts from Aug 15, 2019 regenerated data

\section{Data and Methods} The following sections describe the datasets and initial data exploration 
\subsection{Year slices} Year slices were developed for all publications from 1996-2018. All publications of language 'English' and with at-least 2 references and complete publication data in Scopus are selected. Publications type include (article, conference paper, dissertation etc) and belong to subject area 'COMP'. 
%\vspace{-7mm}
\begin{table}[ht]
\caption{Summary of base Scopus Analytical data set. The number of unique publications, unique references, total references . } 
\label{tab:summary_data}
\centering
\scalebox{0.7}{
\begin{tabular}{|r  ccc |}
  \hline
Year & Unique Publications & Unique References  & Total References \\ 
  \hline
1996 & 30,740 & 184,617 & 318,700 \\ 
1997 &37,166 & 228,464 & 386,627 \\
1998 & 44,764 & 250,491 & 438,908 \\
1999 & 40,434 & 237,175 & 413,681 \\
2000 & 44,636 & 261,393 & 460,310 \\
2001 & 62,000 & 343,937 & 619,330 \\
2002 & 71,645 & 394,882 &722,278 \\
2003 & 83,676 & 438,498 & 849,950 \\
2004 & 82,914 & 482,475 & 915,997 \\
2005 & 107,905 & 591,784 & 1,193,198 \\
2006 & 139,379 & 713,924 & 1,531,101 \\
2007 & 170,396 & 829,444 & 1,830,944 \\
2008 & 204,084 & 1,000,790 & 2,226,980 \\
2009 & 239,113 & 1,222,312 & 2,790,194 \\
2010 & 254,763 & 1,374,471 & 3,164,912 \\
2011 & 255,144 & 1,519,064 & 3,419,719 \\
2012 & 170,364 & 1,374,757 & 2,785,900 \\
2013 & 195,008 & 1,606,955 & 3,353,390 \\
2014 & 264,968 & 1,863,488 & 4,260,613 \\
2015 & 297,534 & 2,037,838 & 4,762,036 \\
2016 & 305,372 & 2,217,138 & 5,140,149 \\
2017 & 291,481 & 2,349,259 & 5,262,725 \\
2018 & 316,495 & 2,623,449 & 6,009,386 \\
 \hline
\end{tabular}}
\vspace{-1mm}%Put here to reduce too much white space after your table 
\end{table}

>>>>

\section{Data and Methods} The following sections describe the datasets and initial data exploration 
\subsection{Year slices} Year slices were developed for all publications from 1996-2018. All publications of language 'English' and with at-least 2 references and complete publication data in Scopus are selected. Publications type include (article, conference paper, dissertation etc) and belong to subject area 'COMP'. 
%\vspace{-7mm}
% latex table generated in R 3.5.1 by xtable 1.8-4 package
% Thu Aug 15 14:13:47 2019
\begin{table}[ht]
\caption{Summary of initial Scopus Analytical data set. The number of unique publications, unique references, total references . } 
\label{tab:summary_data}
\vspace{1mm}
\centering
\scalebox{0.7}{
\begin{tabular}{|r rrr r|}
  \hline
 & Year & Unique Publications & Unique References & Total References \\ 
  \hline
1 & 1996 & 30783 & 185816 & 320533 \\ 
  2 & 1997 & 37284 & 230475 & 389779 \\ 
  3 & 1998 & 45198 & 254160 & 445703 \\ 
  4 & 1999 & 40776 & 241013 & 420839 \\ 
  5 & 2000 & 45310 & 266764 & 471079 \\ 
  6 & 2001 & 65168 & 357472 & 651196 \\ 
  7 & 2002 & 75583 & 410290 & 761714 \\ 
  8 & 2003 & 88701 & 458459 & 904755 \\ 
  9 & 2004 & 88984 & 506063 & 980388 \\ 
  10 & 2005 & 110741 & 609294 & 1247543 \\ 
  11 & 2006 & 140729 & 731622 & 1579690 \\ 
  12 & 2007 & 171357 & 845569 & 1879419 \\ 
  13 & 2008 & 205852 & 1019330 & 2281452 \\ 
  14 & 2009 & 239905 & 1239406 & 2841795 \\ 
  15 & 2010 & 255254 & 1391036 & 3214371 \\ 
  16 & 2011 & 255633 & 1534865 & 3464829 \\ 
  17 & 2012 & 264011 & 1700862 & 3845051 \\ 
  18 & 2013 & 261442 & 1866133 & 4199482 \\ 
  19 & 2014 & 272711 & 2004406 & 4581855 \\ 
  20 & 2015 & 309446 & 2220732 & 5202960 \\ 
  21 & 2016 & 316430 & 2422531 & 5630283 \\ 
  22 & 2017 & 308102 & 2622125 & 5918274 \\ 
  23 & 2018 & 340221 & 3012740 & 6960056 \\ 
   \hline
\end{tabular}}
\vspace{-1mm}
\end{table}
